Moral Foundations of U.S. Political News Organizations

### 2019-03-10 pilot_manuscript.Rmd
filled in progress issues; minor changes to thesis script

  ##save the data
  HuffPoDF$Source[i] = "Huffington Post"
  HuffpoDF$Url[i] = urlslist4[i]
  HuffpoDF$Text[i] = paste(text_data4, collapse = "")
} ##end for loop
```

@@

````{r Fox News, eval = F, include = F}
url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&sort=latest&start=0'
webpage6 = read_html(url6)
headline_data6 = html_nodes(webpage6, 'h3 .ng-binding')

@@

````{r Breitbart, eval = F, include = F}
url7 = 'http://www.breitbart.com/big-government/'
webpage7 = read_html(url7)
headline_data7 = html_nodes(webpage7, '.gs-title')

@@

urlslist7 = unlist(attr_data7)
urlslist7 = urlslist4[grep(urlslist7)]

@@

````{r Rush Limbaugh, eval = F, include = F}
url8 = 'https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1'
webpage8 = read_html(url8)
headline_data8 = html_nodes(webpage8, '.ais-hits--content a')

@@

````{r Sean Hannity, eval = F, include = F}
url10 = 'https://www.theblaze.com/search/?q=kavanaugh'
webpage10 = read_html(url10)
headline_data10 = html_nodes(webpage10, '.gs-title')

>>>>

  ##save the data
  HuffpoDF$Source[i] = "Huffington Post"
  HuffpoDF$Url[i] = urlslist4[i]
  HuffpoDF$Text[i] = paste(text_data4, collapse = "")
} ##end for loop
```

@@

````{r Fox News, eval = F, include = F}
url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=0'
webpage6 = read_html(url6)
headline_data6 = html_nodes(webpage6, 'h3 .ng-binding')

@@

````{r Breitbart, eval = F, include = F}
url7 = 'https://www.breitbart.com/search/?s=kavanaugh#gsc.tab=0&gsc.q=kavanaugh&gsc.page=1'
webpage7 = read_html(url7)
headline_data7 = html_nodes(webpage7, '.gs-title')

@@

urlslist7 = unlist(attr_data7)
urlslist7 = urlslist7[grep(urlslist7)]

@@

````{r Rush Limbaugh, eval = F, include = F}
url8 = 'https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1'
webpage8 = read_html(url8)
#headline_data8 = html_nodes(webpage8, 'a')    trying something different
headline_data8 = html_nodes(webpage8, '.ais-hits--content a')

@@

````{r Sean Hannity, eval = F, include = F}
url10 = 'https://www.hannity.com/'
webpage10 = read_html(url10)
headline_data10 = html_nodes(webpage10, '.gs-title')
